\documentclass[10pt,twoside,twocolumn]{article}
\usepackage[bg-none]{dnd/dnd}	%options: bg-a4, bg-letter, bg-full, bg-print; default are bg-letter and bg-full
\usepackage[utf8]{inputenc}

\title{Dunmar: Ernest's Campaign}
\author{Ernest "edg3" Loveland}

% Start document
\begin{document}
\fontfamily{ppl}\selectfont % Set text font

% Content goes after this
\maketitle
\tableofcontents

\section{About this Document}
This document serves as a record of the campaign I run using the Dunmar DM Guide for my players.

\section{The Standard Campaign}
The standard campaign is a log of the campaign run by Ernest "edg3" Loveland for his party, your mileage may vary with this campaign directly as parts of it were tailored to the specific strengths and weaknesses of the party present. Similarly there are a handful of fixed events listed below which are likely to occur differently. The standard campaign is aimed at being more of a guide to using this setting rather than a direct campaign you can run for your PCs.

\section{About the characters}
\subsection{Arthur}
Played by Luke.\\

Arthur is a human ranger, his family were also rangers and he followed in their path. They mysteriously dissapeared (feycursed), and as he grew he decided he needed to look after some land. He found a noble with considerable land and begun to tend the lands for him, but over time in travels through the wooded lands he began to realise that the land was changing around him.\\

He began to spend more and more time exploring the changing wood until one day he was visited by a spirit that proclaimed "Arthur, you have unfortunately gone astray my child. You are no longer in the plane of existance that you once belonged to and you are trapped here. I will give you a token that marks you as one of a secret organisation inside this world that follows me - they will help you as you bear this mark." Arthur felt a tightening on one of his fingers and found he had a ring (Ring of Thel'm). \\

Arthur ended up surfacing in the forest between Darkwell and Ramshorn and joining random travellers eventually ended up in Bertertun with Du'ruk's caravan heading to Dunmar. \\

\subsection{Viper}
Played by Simon. \\

Viper is a human fighter that used to be a foot-soldier in the army of Mossley. He became dissilusioned with what was happening and tired of being in the army and decided to explore the world. He was not specifically Valar oriented but was well acquainted with the standard uniforms and looks of Valar members. \\

As a family heirloom he owns the sword "Flaming Biter" the sword over time always reverts to its normal form which is warped and rusted but is always deathly sharp. The sword grows more beautiful and well-kept in appearance with the shedding of blood. \\

\subsection{Zack}
Played by Craig. \\

Zack as a young child became interested in magic and while living on Upcrust met a wizard by the name of [check-in-setting] who specialised in teleportation magic. Zack began his apprenticeship under the wizard and after learning the basics (in Butterpond, a magical city) was teleported to Upcrust to begin an explorative journey and learn more about the world.\\

When he left home with [wizard-name] his parents gave him an oddly made key. (see [item-name]) \\

\subsection{Lego-Lass}
Played by Sam. [name-pending] \\

An elf that came from the original material plane [name] is very withdrawn and secretive, not usually willing to divulge secrets of her past life. [name] has only been in Rengar for a few short years and is seeking a way back to the material plane. \\

One of the artifact that [name] has in her possetion is the magical Arrow of Azeal (see items) bestowed by Azeal - the god of chaos. [name] actively seeks revenge on the factions that cast her into Rengar. \\

\section{Story}

\subsection{Session 1: Introduction - Welcome to Dunmar}

\begin{quotebox}
"Welcome to Dunmar," proclaims the gruff man leading the caravan. You met him as Du'ruk, a barbaric looking man veiled in a mystery he created for himself. He only shared with you his first name as he invited you to join his caravan headed to the wonderous city of Dunmar, and over the past few weeks you have built your own suspicions that he was hiding the fact he was actually a half-orc under the various cloths he covered himself with.

As you come closer behind him the valley opens up before you. Bordered on 3 sides by mountains. On the far side you see the majestic city of of Dunmar. Its glorious peaks and towers of the main keep rising high above a city squatted on the side of a mountain.

This world, Renga, is a mess. Split into two domains, the light and vast Upcrust and the dangerous dark lands of Lowcrust. Your journey starts here and within the caravan chatter begins to pick up as people get more excited about being near the end of their long journey.
\end{quotebox}

At this point let the party describe their characters and share with one another the information they have chosen to share. Once they are done describe how over time they draw nearer to the city, at this point in time it makes sense to explain to them a little bit of how the world works.

\begin{quotebox}
Renga is quite a small world if you compare it to most, to travel all the way around the world on Upcrust it will take a little over 3 months by foot, and as such this means when big things happen they happen fast. At the edges of the land-masses making up Upcrust are sheer cliffs dropping down to the wintery wasteland of Lowcrust. While Upcrust is summery and warm and has only a single large body of water beside all of its networks of rivers Lowcrust is the polar opposite - most of Lowcrust is large seas of frozen water and where the cliffs lead up to Upcrust there are huge cave networks containing strange and terrible beasts. There are only two cities on Lowcrust but they are monolithic expanses that take days to travel through.

Let us head back to your travels, as you grow nearer to Dunmar the road you were following widens and various carts carrying different goods to different parts of the valley pass in both directions. Nearing the edge of the city vendors with their carts are calling out with their wares "fresh fish, caught this morning...". "fruits, healthy for the soul..", "spell components, get your magical means fulfilled here..." the caravan heads through without losing speed.

As you get to the gates at the outer wall you notice a party of armored men making a beeline to you. Their armor decorated with copper images of lions they quickly meet up with the caravan. With a booming voice the leader exclaims "my friend Du'ruk, it has been too long!" he removes his helmet after dismounting his horse and embraces Du'ruk. The man is heavily built and looks like pure muscle, his flowing red hair and beard you would not have believed would fit in his helmet had he not just taken it off. "Ah Renton, maybe not long enough" Du'ruk replies. The step to the side and have a jovial conversation littered with laughter and tom-foolery, it is clear they are old friends.

One of the soldiers that arrived with Renton begins to inspect the wagons and the people that you traveled with while the other reads from a scroll, "Welcome to Dunmar, there are a few important rules we need to make clear to you before you run free in out city.." - he essentially rambles on but you get the gist of it. The city is happy for you to do anything as long as it respects the people around you and after the third chime of the church bell after sundown not to make noise. The inspection ends fairly quickly and it is obvious this is a place of peace, they aren't expecting trouble from anyone and are ready to move on to more important matters.

Du'ruk turns to the caravan and leads you to a nearby inn, you are told the first night is complementary. You take your things to your rooms and meet up for a hearty dinner. In the common room you are treated to a hearty beef stew, all the beer you can drink and being tired from travelling you all head to bed soon after your fantastic evening entertainment.
\end{quotebox}

Let your PCs explain how they sleep, and how they feel and make a rool for passive perception throughout the night.

First check: DC 15 Perception - whomever passes this check is awoken, in the distance you can hear something that does not sound like a quiet city night. Checking outside through a window you can hear towards the gate you entered the city there is some commotion, nothing completely out of hand but there is definitely some small fight.

Second check: DC 10 Perception - whomever passes this check is now alert, there are definitely sounds outside near the inn that shouldnt occur in these late hours of the night. Looking outside people will see a party of hooded figures stealthily advancing down the road past the inn, every person they come in contact with they are poking with a a needle and the people are falling unconscious.

Third check: When any played confronts or tries to fight a hooded figure there will be a cry, and this wakes up the rest of the PCs.

In the road in front of the inn passing are 6 hooded figures (DM note: these are all minions of Illuminated - 4 squire of Bristlebow [lv.1 minion] and 2 archer of bristlebow [lv.2 minion knight] - they will try to be peaceful towards the PCs. Special mechanics their attacks are replaced with "Knock Out Needle" see below).

In passing hooded figures in range will try hit anyone in their way with a "Knock Out Needle", on a successful hit on a PC they will realise that the PCs are not "Worldly" beings and their leader will try talk to the PCs (see below), similarly if a PC downs one of the hooded figures with an attack they will stop running past and back off and try use their "Knock Out Needle" avoiding combat. They are lightly armed so easier to hit but also dodge attacks with advantage.

% TODO: ability box
% TODO: item box
\begin{itembox}{Knock Out Needle}
	\textit{A small non-lethal poisoned needle.}\\
	\hline \\[1mm]
	\begin{itemaction}[Action: Jab]
		Jab a character with a neede to try knock them out.\\
		Roll 1d20+5 to hit versus AC:\\
		Hit on wordly character: the character is instantly knocked out.\\
		Hit on PC or unworldly character: the character becomes drowsy and actions are taken at a disadvantage for 5 minutes
	\end{itemaction}
\end{itembox}

It is nearly innevitable that the players will attempt to use some form of magic. This will trigger a magical trap (several of which are hidden around the city) which launches a red flair into the air above the city and calls for guards from the garisson to come and stop whomever is breaking the magic-after-dark rules of Dunmar. \\

The players opted to hide from the figures (and succeeded), they hid inside their room inside the inn and waited for them to pass. Shortly after 3 people in red leather (valar lv. 1 minions) came past and the players overheard as these guys ran past (not bothering to be very quiet or subtle, saying "...they're going to spring the prisoner..." - knowing this to be a bad thing the PCs decided to follow the red-cloaked figures. \\

Outside the jailhouse the PCs snuck up to the Valar people and asked what was happening. They were filled in about trying to stop the illuminated people (in the black cloaks) as they were directly opposing factions wanting the same goal but in disagreement with methods. The players then learned that of the two groups the Valar were openly more miliataristic. \\

The players decided to help the Valar fighters to stop the Illuminated from freeing their friend, they quickly knocked out the Illuminated but to their dismay the mage Zack forgot that magic was prohibitted in the streets at night and set of a magic detection trap that alerted the city guard. \\

The players managed to finish combat before the guard arrived, and the session was brought to an end there.

\paragraph{End of Session 1 Notes}
The characters were given special items and their background bringing them together was fleshed out - they stayed in the inn together. \\

The PCs currently have 4 points towards Valar, 0 to Worldly and Illuminated.

\subsection{Level 1 Improvising}
\paragraph{Creatures}

\textbf{Damage:} 1d4 for light damage, 1d8 for medium, 1d8+2 for heavy damage.\\
\textbf{AC:} 10 for light, 12 for medium, 14 for high.\\
\textbf{Health:} 5 for minions, 7 for heavy minions.\\

For the session I specifically chose to keep it simple to keep things flowing and fast, in future encounters will be more difficult. \\

\subsection{Session 2 - Escaping the Long Arm of Dunmar Law}

Beginning the session we will have the party running away from the guard, every failure brings the guard one step closer to the players [they are 4 failures behind] where as each success is one step further from the guards [their lead needs to be 12 or more]. \\

Additional notes for the first skill challenge:
\begin{itemize}
\item If Arthur looks for another route Arthur will have advantage on his perception check and on DC 10 and above find an alleyway and on DC 15 see a doorway with a Thel'm marking.
\end{itemize}

If they find and go into the room of Thel'm there will be a diary decribing sundry visits and a note on the desk saying that members of Thel'm may stay here as long as they wish, the owner visits once or twice a week for any that want to make contact with the owner. The owner will actually be one of the Illuminated from the previous night and recognise the PCs.\\

If they end up passing and following the Valar members they will be in a Valar owned bar, be given free lodging and be told one of the higher-ups will be visiting the next day and they can talk to that person. \\

If they choose to just run elsewhere you will need to improvise further - see the Level 1 Improvising table for enemies. At this stage of their journey there wont be large-scale difficult battles.\\

If they end up being caught they will be caught by the guard and jailed next to the Illuminated spy that had been captured.\\

% End Document
\end{document}
