\documentclass[10pt,twoside,twocolumn]{article}
\usepackage[bg-none]{dnd/dnd}	%options: bg-a4, bg-letter, bg-full, bg-print; default are bg-letter and bg-full
\usepackage[utf8]{inputenc}

\title{Dunmar: Items}
\author{Ernest "edg3" Loveland}

% Start document
\begin{document}
\fontfamily{ppl}\selectfont % Set text font

% Content goes after this
\maketitle
\tableofcontents

% TODO: item box
\begin{itembox}{Silver Ring of Thel'm}
	\textit{Level 3. An artifact of the Lowcrust people, a very secretive society who will only allow members (such as this one) to use their means of travel and attend their secret meetings.}\\
	\hline \\[1mm]
	\begin{itemaction}[None.]
		This item has no known action.
	\end{itemaction}
\end{itembox}

\begin{itembox}{Flaming Biter}
	\textit{Level 2. An ancient blade that thirsts for destruction, it's blade is rusted and warped but still extremely sharp. As enemies are slain the blade becomes cleaner and straighter.}\\
	\hline \\[1mm]
	\begin{itemaction}[Attack.]
		Melee Weapon Attack: +3 to hit 1d6+4 damage. \\
		
		On an 18-20: +2d4 fire damage. \\
	\end{itemaction}
\end{itembox}

\begin{itembox}{Arrow of Azeal}
	\textit{Level 3. An ornate golden arrow, light as a feather.}\\
	\hline \\[1mm]
	\begin{itemaction}[Use.]
		Arrow of Azeal can be used with any standard bow attack, on an 18-20 Arrow of Azeal deals +1d4 radiant damage to the enemy it strikes. \\
	\end{itemaction}
	\begin{itemaction}[Recall.]
		Bonus Action. As a bonuc action after an attack you may recall the Arrow of Azeal. \\
		
		If the Arrow of Azeal struck an opponent and is now being returned as it returns it deals +1d4 damage to that enemy.
	\end{itemaction}
\end{itembox}

% End Document
\end{document}